\documentclass[addpoints,12pt]{exam}
\printanswers
\usepackage{amsmath,amssymb,complexity,amsthm}
\usepackage{graphicx}
\usepackage[linesnumbered]{algorithm2e}
\usepackage{mathtools}
\usepackage{tkz-graph}
\DeclareMathOperator*{\argmin}{argmin}  

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{titling}
\usepackage{multicol}
\usepackage{pgfplots} 
\usepackage{physics}
\pgfplotsset{width=10cm,compat=1.9} 
\usepgfplotslibrary{external}
\tikzexternalize
\pointpoints{mark}{marks}
\renewcommand{\solutiontitle}{\noindent\textbf{}\par\noindent}

\addtolength{\oddsidemargin}{-.5in}
\addtolength{\textwidth}{.8in}
\addtolength{\topmargin}{-0.25 in}
\addtolength{\textheight}{0.4in}
\title{CS6745: Mining Massive DataSets}
\author{\large \textbf{Assignemnt 2 Report} }

\begin{document}

%\vspace{-7cm}
\vspace{1.5mm} Name : Pawan Bathe \hspace{8cm} Roll No.:CS18M519 \tabuarnewline \vspace{1.5mm} \hline
\vspace{2mm}
\begin{center}
{\Large \thetitle\\}
\vspace{2mm}
{\large \theauthor\\}
\vspace{2mm}
{\large \thedate}
\end{center}
% \maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}

    \question How does the jaccard similarity estimated using minhashing vary when the number of rows is varied?

\begin{solution}

Jaccard similarity estimated using minhashing decreases when numbers of rows are increased. 

\end{solution}

\vspace{3mm}

\question How much do the calculated jaccard similarity and the estimated similarity vary?
\begin{solution}

Calculated  jaccard similarity and the estimated similarity  do not vary much, they are nearly equal. 

\end{solution}

\question How does the performance of LSH compare to brute-force, with respect to average similarity and running time?
\begin{solution}
Average similarity of brute force approach is better.
Also LHS  running time is more than brute force approach.
Time increase when number of permutations are increased.  

\end{solution}

\vspace{3mm}

\question How does this vary with dataset size, k, r, and number of rows in signature matrix?

\begin{solution}
Running time increases with increase in dataset size, k, r and number of rows in signature matrix.
Average similarity decreases with increase n dataset size, k, r and number of rows in signature matrix.

\end{solution}
\end{questions}
\end{document}